---
title: "HCP depressions 2"
output: html_notebook
---

```{r}
library(plyr)
library(vroom)
library(tidyselect)
```

```{r}
p_corr<-function(p){
  val = 1 - p 
}

tf<-function(df,x){
  mat = matrix(df[x,], nrow = 15,ncol = 15)
  return(mat)
}

x<-c(1,2,3,4,5,6,7,8,9,10,11)  
x<-as.data.frame(t(x))

finder<-function(df, liist){
  #threshDF<-sapply(df, p_corr)
  sigDF<-df <= 0.05 
  for (i in x){
  new_element<-tf(sigDF, i)
  liist[[i]] <- new_element
  }
  return(liist)
}

```

```{r}
listofiles<-list.files(path = "~/Google Drive/HCP/HCP_graph/1200/datasets/depress/results/results/", pattern = "p*.txt")
listofiles<-listofiles[-c(1, 2, 3, 4, 9,10,11,12,13,14,15,16)]
listofiles <- paste("~/Google Drive/HCP/HCP_graph/1200/datasets/depress/results/results/", listofiles,sep="")

df <- vroom( listofiles, id = "ID", col_names = FALSE)
df<- df %>% 
  mutate(across(where(is.character), str_remove_all, pattern = fixed("~/Google Drive/HCP/HCP_graph/1200/datasets/depress/results/results/"))) %>%
  mutate(across(where(is.character), str_remove_all, pattern = fixed(".txt"))) 
contrasts<-c("mean","pos int","neg int","pos dep","neg dep","pos BMI","neg BMI","pos symp","neg symp","pos Hb","neg Hb")

df<-df %>% 
  group_by(ID) %>%
  mutate(contrasts = contrasts)
dim(df)[1]
df[2:226]<-1-df[2:226]
df$ID
```

```{r}
AX<-subset(df, df$ID == "pAX")
DT<-subset(df, df$ID == "pDT")
AXhb<-subset(df, df$ID == "pAXhb")
DThb<-subset(df, df$ID == "pDThb")
dim(AX)
```

```{r}
listAX <- list()
tAX<-finder(as.data.frame(AX[2:226]), listAX)
tAX[[3]]
```
# Positive interaction with BMI and anxiety 
IC 4 (visual)  and 8 (cerebellum) t= 3.8726
IC 13 (Mouth somatosensory) and 8 (cerebellum) t= 3.6826
# Negative interaction with BMI and anxiety
IC 1 (visual) and 11 (DAN) t= 3.7938
IC 1 (visual) and 13 (Mouth somatosensory) t= 3.8089
IC 2 (DMN) and 8  (cerebellum) t= 3.4972
IC 13 (Mouth somatosensory) and 11 (DAN) t= 3.3511
```{r}
tlistAX <- list()
ttAX<-tfinder(as.data.frame(tAX[2:226]), tlistAX)
ttAX[[2]]
```

```{r}
listAXhb <- list()
tAXhb<-tfinder(as.data.frame(AXhb[2:226]), listAXhb)
tAXhb[[3]]
```
```{r}
tlistAXhb <- list()
ttAXhb<-tfinder(as.data.frame(tAXhb[2:226]), tlistAXhb)
ttAXhb[[3]]

t2r<-function(t, n){
  DF = n-1
  Rsq = t^2 / (t^2 + DF)
  return (sqrt(Rsq))
  }
t2r(4.4721, 325)
```
# Positive interaction with HbA1c and anxiety
IC 1 (visual) and 8 (cerebellum) t= 3.7562, r= 0.2042774
IC 4 (visual/DAN) and 8 (cerebellum) t= 3.3986  r= 0.185533
IC 9 (DMN) and 8 (cerebellum) t=  3.3273
IC 13 (Mouth somatosensory) and 8 (cerebellum) t= 4.291
# Negative interaction with HbA1c and anxiety
IC 1 (visual) and 11 (DAN) t= 3.8679
IC 1 (visual) and 13 (Mouth somatosensory) t= 4.5622
IC 7 (FPN, DMN) and 8 (cerebellum) t= 3.4514
IC 9 (DMN) and 10 (VAN/DMN) t= 3.7291  
IC 11 (DAN) and 13 (Mouth somatosensory) t= 4.4721 

```{r}
listDT <- list()
DT[2:226]
tDT<-finder(as.data.frame(DT[2:226]), listDT)
tDT<-tfinder(as.data.frame(DT[2:226]), listDT)

tDT[[3]]
```
```{r}
tlistDT <- list()
ttDT<-tfinder(as.data.frame(tDT[2:226]), tlistDT)
ttDT[[3]]
t2r(3.6456, 325)
```
# positive interaction with depression and BMI
IC 4 (visual/DAN) and 8 (cerebellum) t= 3.4061  
IC 5 (FPN) and 7  (FPN, DMN) t= 3.3702
IC 5 (FPN) and 14 (Salience FPN) t= 3.565
IC 8 (cerebellum) and 13 (Mouth somatosensory) t= 4.0497
# negative interaction with depression and BMI
IC 1 (visual) and 13 (Mouth somatosensory) t= 3.394
IC 11 (DAN) and 13 (Mouth somatosensory) t= 3.6456

```{r}
listDThb <- list()
DThb[2:226]
tDThb<-finder(as.data.frame(DThb[2:226]), listDThb)
tDThb[[10]]
```
# Positive interaction with HbA1c and depression
None
# Negative interaction with HbA1c and depression
None



```{r}
listofiles<-list.files(path = "~/Google Drive/HCP/HCP_graph/1200/datasets/depress/results/results/", pattern = "p*.txt")
listofiles<-listofiles[-c(1,2,3,4,5,6,7,8,13,14,15,16)]
listofiles <- paste("~/Google Drive/HCP/HCP_graph/1200/datasets/depress/results/results/", listofiles,sep="")
tdf <- vroom( listofiles, id = "ID", col_names = FALSE)
tdf<- tdf %>% 
  mutate(across(where(is.character), str_remove_all, pattern = fixed("~/Google Drive/HCP/HCP_graph/1200/datasets/depress/results/results/"))) %>%
  mutate(across(where(is.character), str_remove_all, pattern = fixed(".txt"))) 
contrasts<-c("mean","pos int","neg int","pos dep","neg dep","pos BMI","neg BMI","pos symp","neg symp","pos Hb","neg Hb")
tdf
```


```{r}
tAX<-subset(tdf, tdf$ID == "tAX")
tDT<-subset(tdf, tdf$ID == "tDT")
tAXhb<-subset(tdf, tdf$ID == "tAXhb")
tDThb<-subset(tdf, tdf$ID == "tDThb")
dim(tAX)
```

```{r}
tf<-function(df,x){
  mat = matrix(df[x,], nrow = 15,ncol = 15)
  return(mat)
}

x<-c(1,2,3,4,5,6,7,8,9,10,11)  
x<-as.data.frame(t(x))

tfinder<-function(df, liist){
  for (i in x){
  new_element<-tf(df, i)
  liist[[i]] <- new_element
  }
  return(liist)
}

```



