---
title: "HCP depressions 3"
output: html_notebook
---

```{r}
library(vroom)
library(stringr)
library(plyr)
library(dplyr)
library(data.table)
library(ggpubr)
library(psych)
```

```{r}
unres<-read.table("~/Google Drive/HCP/HCP_graph/1200/datasets/unrestricted_gshearrer_4_19_2018_11_31_37.csv", header=T, sep=",")
res<-read.table("~/Google Drive/HCP/HCP_graph/1200/datasets/RESTRICTED_gshearrer_4_19_2018_11_33_34.csv", header=T, sep=",")
beh<-join(unres, res)
interest<-c("Subject", "DDisc_AUC_200","DDisc_AUC_40K", "Taste_AgeAdj", "CardSort_AgeAdj","Flanker_AgeAdj"  )
beh<-beh[interest]
```


```{r}
scan_df<-vroom("~/Google Drive/HCP/HCP_graph/1200/datasets/depress/scan_df.csv")
# Find tertiles
hbTert = quantile(scan_df$HbA1C, c(0:3/3))
hbTert

# classify values
scan_df$tert = with(scan_df, 
               cut(HbA1C, 
                   hbTert, 
                   include.lowest = T, 
                   labels = c("Low", "Medium", "High")))
head(scan_df$HbA1C)
```

```{r}
setwd("~/Google Drive/HCP/HCP_graph/1200/datasets/depress/results/results/")
files <- fs::dir_ls(glob = "netamts*.txt")
files
NM<-vroom(files, col_names = F, id = "path")
NM$Flavor<-str_remove(NM$path, ".txt")

colz<-vroom("~/Google Drive/HCP/HCP_graph/1200/datasets/depress/colnames.csv")

new<-names(colz)
old<-colnames(NM[2:226])

setnames(NM, old = old, new = new)
cbPalette <- c("red3", "midnightblue", "pink")

```

```{r}
setwd("~/Google Drive/HCP/HCP_graph/1200/datasets/depress/node_timeseries/3T_HCP1200_MSMAll_d15_ts2/")
files <- fs::dir_ls(glob = "*.txt")
files
t_s<-vroom(files, col_names = F, id = "path")

t_s$Subject<-str_remove(t_s$path, ".txt")
total_df<-join(scan_df, t_s)
names(total_df)
```

```{r}
df<- total_df %>%
  group_by(Subject, tert) %>%
  summarise(mean1 = mean(X1),
            mean2 = mean(X2),
            mean3 = mean(X3),
            mean4 = mean(X4),
            mean5 = mean(X5),
            mean6 = mean(X6),
            mean7 = mean(X7),
            mean8 = mean(X8),
            mean9 = mean(X9),
            mean10 = mean(X10),
            mean11 = mean(X11),
            mean12 = mean(X12),
            mean13 = mean(X13),
            mean14 = mean(X14),
            mean15 = mean(X15),
            meanHb = mean(HbA1C))
head(df)
df<-join(df, beh)
scan_df<-join(scan_df, beh)
```

```{r}
names(scan_df)
```


```{r}
p1<-ggplot(subset(df, df$tert != "Medium"), aes(mean8, mean1, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="IC 1")+
  scale_x_continuous(name="IC 8")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic() + 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
p1

p2<-ggplot(subset(df, df$tert != "Medium"), aes(mean8, mean4, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="IC 4")+
  scale_x_continuous(name="IC 8")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic() + 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
p2

p3<-ggplot(subset(df, df$tert != "Medium"), aes(mean8, mean7, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="IC 7")+
  scale_x_continuous(name="IC 8")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic() + 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
p3

p4<-ggplot(subset(df, df$tert != "Medium"), aes(mean8, mean13, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="IC 13")+
  scale_x_continuous(name="IC 8")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic() + 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
p4
```







```{r}
NMAX<-subset(NM, NM$Flavor == "netamts1AX")%>%
  cbind(.,scan_df)
NMAXhb<-subset(NM, NM$Flavor == "netamts1AXhb")%>%
  cbind(.,scan_df)
NMDT<-subset(NM, NM$Flavor == "netamts1DT")%>%
  cbind(.,scan_df)
NMDThb<-subset(NM, NM$Flavor == "netamts1DThb")%>%
  cbind(.,scan_df)
```


```{r}
names(NMAXhb)
```


```{r}

grouper<-NMAXhb %>%
  group_by(Subject, tert, Gender, Race, Age_in_Yrs) %>%
  summarise(mean_age = mean(Age_in_Yrs, na.rm = TRUE), 
            mean_hba1c = mean(HbA1C, na.rm = TRUE),
            mean_symp = mean(SSAGA_Depressive_Sx, na.rm = TRUE),
            mean_BMI = mean(BMI, na.rm = TRUE ),
            mean_anx = mean(ASR_Anxd_Pct, na.rm = TRUE), 
            mean_motion = mean(motion, na.rm = TRUE),
            mean_1v8 = mean(`1v8`, na.rm = TRUE),
            mean_4v8 = mean(`4v8`, na.rm = TRUE),
            mean_7v8 = mean(`7v8`, na.rm = TRUE),
            mean_13v8 = mean(`13v8`, na.rm = TRUE),
            mean_DDisc_AUC_200 = mean(DDisc_AUC_200, na.rm = TRUE),
            mean_DDisc_AUC_40K = mean(DDisc_AUC_40K, na.rm = TRUE),
            mean_Taste_AgeAdj = mean(Taste_AgeAdj, na.rm = TRUE),
            mean_CardSort_AgeAdj = mean(CardSort_AgeAdj, na.rm = TRUE),
            mean_Flanker_AgeAdj = mean(Flanker_AgeAdj, na.rm = TRUE)
            ) 
names(grouper)
```

```{r}
mod1<-lm(mean_DDisc_AUC_40K ~ mean_1v8 + mean_hba1c*mean_anx + mean_age + Gender + Race, data = grouper)
t1<-summary(mod1)  

mod2<-lm(mean_DDisc_AUC_200 ~ mean_1v8 + mean_hba1c*mean_anx + mean_age + Gender + Race, data = grouper)
t2<-summary(mod2) 
```

```{r}
mod3<-lm(mean_DDisc_AUC_40K ~ mean_4v8 + mean_hba1c*mean_anx + mean_age + Gender + Race, data = grouper)
t3<-summary(mod3) 


mod4<-lm(mean_DDisc_AUC_200 ~ mean_4v8 + mean_hba1c*mean_anx + mean_age + Gender + Race, data = grouper)
t4<-summary(mod4) 
```

```{r}
mod5<-lm(mean_DDisc_AUC_40K ~ mean_7v8 + mean_hba1c*mean_anx + mean_age + Gender + Race, data = grouper)
t5<-summary(mod5)  

mod6<-lm(mean_DDisc_AUC_200 ~ mean_7v8 + mean_hba1c*mean_anx + mean_age + Gender + Race, data = grouper)
t6<-summary(mod6) 

lm.beta(mod6)
```

```{r}
mod7<-lm(mean_DDisc_AUC_40K ~ mean_13v8 + mean_hba1c*mean_anx + mean_age + Gender + Race, data = grouper)
t7<-summary(mod7)  

mod8<-lm(mean_DDisc_AUC_200 ~ mean_13v8 + mean_hba1c*mean_anx + mean_age + Gender + Race, data = grouper)
t8<-summary(mod8) 
t8
library(lm.beta)
lm.beta(mod8)
```

# correction for multiple comparisons
```{r}
all2<-rbind(t1$coefficients[,4], t2$coefficients[,4], t3$coefficients[,4], t4$coefficients[,4], t5$coefficients[,4], t6$coefficients[,4], t7$coefficients[,4], t8$coefficients[,4])
dim(all2)
all2
adj_p<-p.adjust(all2, method = "BH")
adj_p
adj_p[14]

# 14, 16 significant
# mod 6 and mod 8 mod 2
```
Area under the curve values range from 0 to 1; 
higher AUC values indicate lower discounting by delay (i.e., a preference for delayed, larger rewards)
lower AUC values correspond to steeper, or more impatient, discounting (i.e., a preference for smaller, more immediate rewards)
```{r}
pmod6<-ggplot(subset(grouper, grouper$tert != "Medium"), aes(mean_7v8, mean_DDisc_AUC_200, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="Delay discounting $200 AUC")+
  scale_x_continuous(name="Correlation between IC 7 and 8")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic() + 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
pmod6


pmod8<-ggplot(subset(grouper, grouper$tert != "Medium"), aes(mean_13v8, mean_DDisc_AUC_200, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="Delay discounting $200 AUC")+
  scale_x_continuous(name="Correlation between IC 13 and 8")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic() + 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
pmod8

ggsave("pmod6_7v8.png", plot = pmod6, path = "~/Google Drive/HCP/HCP_graph/1200/datasets/depress/brains/",width = 7, height = 6, units = "in")

ggsave("pmod6_13v8.png", plot = pmod8, path = "~/Google Drive/HCP/HCP_graph/1200/datasets/depress/brains/",width = 7, height = 6, units = "in")

```



```{r}
p4<-ggplot(subset(grouper, grouper$tert != "Medium"), aes(mean_1v8, mean_DDisc_AUC_200, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="Delay discounting 200")+
  scale_x_continuous(name="1v8")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic() + 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
p4

p4<-ggplot(subset(grouper, grouper$tert != "Medium"), aes(mean_1v8, mean_DDisc_AUC_40K, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="Delay discounting 200")+
  scale_x_continuous(name="1v8")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic() + 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
p4

```

```{r}
describeBy(NMAXhb$HbA1C, NMAXhb$tert)
```

# Positive interaction with HbA1c and anxiety
IC 1 (visual) and 8 (cerebellum/Hippocampus) t= 3.7562, r= 0.2042774
IC 4 (visual/DAN) and 8 (cerebellum) t= 3.3986  r= 0.185533
IC 9 (DMN) and 8 (cerebellum) t=  3.3273
IC 13 (Mouth somatosensory) and 8 (cerebellum) t= 4.291

## About IC 8
Vermis Crus I<-process of executive functions, such as working memory, planning, organizing, and strategy formation
Vermis VIIIb<- represent a site where the cortical motor areas can influence descending control systems involved in the regulation of whole-body posture and locomotion, nucleus to the ventral tegmental area (VTA) that also receives Purkinje axons
disinhibition of the mPFC and striatal subdivisions that receive dopaminergic projections, mainly from the VTA. Moreover, cerebellar impairment induced an upregulation
of PNN expression in the mPFC
the posterior cerebellar cortex may exert inhibitory control over the striatum and mPFC

```{r}
NMAXhb<-subset(NMAXhb, NMAXhb$tert != "Medium")

p1<-ggplot(NMAXhb, aes(ASR_Anxd_Pct, `1v8`, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="Correlation between IC1 and IC8")+
  scale_x_continuous(name="Anxiety and Depression")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic() + 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
p1
ggsave("1v8g.png", plot = p1, path = "~/Google Drive/HCP/HCP_graph/1200/datasets/depress/brains/",width = 7, height = 6, units = "in")

p2<-ggplot(NMAXhb, aes(ASR_Anxd_Pct, `4v8`, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="Correlation between IC4 and IC8")+
  scale_x_continuous(name="Anxiety and Depression")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic()+ 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
ggsave("4v8g.png", plot = p2, path = "~/Google Drive/HCP/HCP_graph/1200/datasets/depress/brains/",width = 7, height = 6, units = "in")

p3<-ggplot(NMAXhb, aes(ASR_Anxd_Pct, `9v8`, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm)+scale_y_continuous(name="9 and 8")+
  scale_x_continuous(name="Anxiety and Depression")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic()

p4<-ggplot(NMAXhb, aes(ASR_Anxd_Pct, `13v8`, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="Correlation between \n IC 13 and IC 8")+
  scale_x_continuous(name="Anxiety and Depression")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic()+ 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
ggsave("13v8g.png", plot = p4, path = "~/Google Drive/HCP/HCP_graph/1200/datasets/depress/brains/",width = 7, height = 6, units = "in")

ggarrange(p1, p2, p3, p4, ncol = 2)
```



# Negative interaction with HbA1c and anxiety
IC 1 (visual) and 11 (DAN/somatomotor) t= 3.8679
IC 1 (visual) and 13 (Mouth somatosensory and caudate and Vermis VI) t= 4.5622
IC 7 (FPN including right parietal lobule) and 8 (cerebellum) t= 3.4514
IC 9 (DMN) and 10 (DMN) t= 3.7291  
IC 11 (DAN/somatosensory/Hippocampus) and 13 (Mouth somatosensory) t= 4.4721 
```{r}
NMAXhb<-subset(NMAXhb, NMAXhb$tert != "Medium")
p1<-ggplot(NMAXhb, aes(ASR_Anxd_Pct, `1v11`, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm)+scale_y_continuous(name="1 and 11")+
  scale_x_continuous(name="Anxiety and Depression")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic()

p2<-ggplot(NMAXhb, aes(ASR_Anxd_Pct, `1v13`, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm)+scale_y_continuous(name="1 and 13")+
  scale_x_continuous(name="Anxiety and Depression")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic()

p3<-ggplot(NMAXhb, aes(ASR_Anxd_Pct, `7v8`, colour = tert)) +
  geom_point(shape=1) +
  geom_smooth(method=lm, size = 2)+
  scale_y_continuous(name="Correlation between IC 7 and IC 8")+
  scale_x_continuous(name="Anxiety and Depression")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic()+ 
  scale_color_manual(values = cbPalette)+
  theme(axis.text = element_text(size = 20)) + 
  theme(axis.title.x =  element_text(size = 25)) +
  theme(axis.title.y =  element_text(size = 25)) 
ggsave("7v8g.png", plot = p3, path = "~/Google Drive/HCP/HCP_graph/1200/datasets/depress/brains/",width = 7, height = 6, units = "in")


p4<-ggplot(NMAXhb, aes(ASR_Anxd_Pct, `9v10`, colour = tert)) +
  geom_point(shape=1) +
    geom_smooth(method=lm)+scale_y_continuous(name="Correlation between IC 8 and IC")+
  scale_x_continuous(name="Anxiety and Depression")+
  theme(axis.title.x = element_text( size=20),axis.text.x  = element_text(size=20))+
  theme(axis.title.y = element_text( size=20),axis.text.y  = element_text(size=20))+
  theme_classic()
ggarrange(p1, p2, p3, p4, ncol = 2)
```
# Post hoc
Check delayed discounting AUC 
